Saving boundary datasets for DeepTools

### 2020-09-11 Scripts_for_results/13_saving_boundary_data_for_deeptools.Rmd
addressed todo items

  pred_bound_list[[i]] <- called_and_pred[[2]]
  true_bound_list[[i]] <- called_and_pred[[3]]

@@

length(all_true_bounds) #15468
length(all_pred_bounds) #7846

@@

length(all_true_bounds) #9316
length(all_pred_bounds) #8883

@@

length(all_true_bounds) #21421
length(all_pred_bounds) #15838

@@

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10,11,13:22))
for(i in 1:length(chrs)){
  print(i)
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_holdout_peakachu.rds"))

  pred_bound_list[[i]] <- called_and_pred[[2]]
  true_bound_list[[i]] <- called_and_pred[[3]]

@@

length(all_true_bounds) #20773
length(all_pred_bounds) #10379

>>>>

  pred_bound_list[[i]] <- called_and_pred$PTBP
  true_bound_list[[i]] <- called_and_pred$CTBP

@@

length(all_true_bounds) #15468
length(all_pred_bounds) #12258

@@

length(all_true_bounds) #9316
length(all_pred_bounds) #9603

@@

length(all_true_bounds) #21421
length(all_pred_bounds) #15707

@@

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10,11,13:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_holdout_peakachu.rds"))

  pred_bound_list[[i]] <- called_and_pred$PTBP
  true_bound_list[[i]] <- called_and_pred$CTBP

@@

length(all_true_bounds) #20773
length(all_pred_bounds) #10516
